Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Reference fix

% \copyrightyear{2020} 
% \acmYear{2020} 
% \setcopyright{acmlicensed}
% \acmConference{DISC '20}{October 12-16, 2020}{Freiburg, Germany}

 \keywords{online algorithms, competitive analysis, distributed computing, graph partitioning, clustering, self-adjusting networks}
% \acmISBN{}\acmPrice{}
% \acmDOI{}

 \ccsdesc[500]{Networks~Network algorithms}
 \ccsdesc[300]{Computer systems organization~Cloud computing}
 \ccsdesc[300]{Computer systems organization~Distributed architectures}

@@

The adversary constructs ground sets (a set of nodes that may communicate, see Section~\ref{sec:prelim}) depending on choices of a deterministic online algorithm.
We emphasize that the algorithm does not know ground sets before they are revealed.
Once we construct a ground set, it lasts until the end of the input sequence.

>>>>

 \authorrunning{M. Pacut, M. Parham, and S. Schmid}
 \Copyright{Maciej Pacut, Mahmoud Parham, and Stefan Schmid}
 \keywords{online algorithms, competitive analysis, distributed computing, graph partitioning, clustering, self-adjusting networks}

% \EventEditors{}
%\EventNoEds{3}
 \EventLongTitle{34th International Symposium on DIStributed Computing (DISC) 2020)}
 \EventShortTitle{DISC 2020}
 \EventAcronym{DISC}
 \EventYear{2020}
 \EventDate{October 12--16, 2020}
 \EventLocation{Freiburg, Germany (virtual conference)}
 \EventLogo{}
 \SeriesVolume{}
 \ArticleNo{}

 \ccsdesc[500]{Networks~Network algorithms}
 \ccsdesc[300]{Computer systems organization~Cloud computing}
 \ccsdesc[300]{Computer systems organization~Distributed architectures}
 \ccsdesc[500]{Theory of computation~Online algorithms}

@@

The adversary constructs ground sets depending on choices of a deterministic online algorithm.
We emphasize that the algorithm does not know ground sets before they are revealed.
Once we construct a ground set, it lasts until the end of the input sequence.
